---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# VariantsID

<!-- badges: start -->
<!-- badges: end -->

The goal of VariantsID is to ...

## Installation

You can install the development version of VariantsID like so:

``` r
devtools::install_github("Linda24bc/VariantsID")
```
## Introduction
+ Identify the Hb variants by comparing the experimental data in the database
+ Original database contains the theoretical diagnostic ions of Hb variants been tested by mass spectrometry so far 

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(VariantsID)
```
### Step 1. Input the database including the diagnostic ions of Hb varints and use MS1 data to narrow down the database - subset the database

1.1 Input the original database

HbDatabase <-  read_csv("Hb Variants_OriginalDatabase.csv")

1.2 Use the MS1 data to narrow down the database, if the mass shift is about -0.93 Da, then the Mshift is -0.93 Da and the error tolerence is 0.06 Da. Thoese two values are changable and depend on the accuracy of deconvolution.

ref <- SubDatabase(HbDatabase, Mshift= -0.93, error_Da_L=-0.05, error_Da_R=0.06)

### Step 2. Input the deconvolve MS2 results 
The list should contain two columns,  Exp_m/z vs Exp_Intensity)

exp <- read_csv("expt mass_AC.csv")

### Step 3. Search the experimental results in the subset database with Variant Identifier
Run the function Variants.Identifier, the ppm_error range is changable and depends on the accuracy of the MS2 data. View the result list and get the identification.

ID.results <- Variants.Identifier(ref, exp, ppm_error_start=-2, ppm_error_end=5)

### Step 4. Output the results in .csv

write.csv(ID.results, "ID_HbAE_1.csv", row.names = FALSE)
